---
title: "Hello R"
author: "Jaylene Martinez"
date: "Data 2401"
output: html_document
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

The datasaurus_dozen file has 1846 rows and 3 columns. The variables included are, dataset, x and y values.

### Exercise 2

Plot y vs. x for the dino dataset.

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino") # Filters the datasaurus dozen dataset to include only rows where the dataset column is "dino"
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point() # Visualizing the "dino" dataset by plotting x and y coordinates as a scatter plot
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
#Calculates the correlation (r) between the x and y variables in the "dino" dataset
dino_data %>%
  summarize(r = cor(x, y)) 
```

### Exercise 3

Plot y vs. x for the star dataset:

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter (dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

The scatter plot of the 'star' dataset displays a structured star like pattern. It showcases the importance of visuals in data analysis.

Calculate the correlation coefficient between x and y for this dataset:
 
```{r cor-star}
star_data %>%
  summarize(r = cor(x,y))

```
The correlation (r) for the dino and star dataset is similar despite their visual difference, they both indicate almost no linear relationship. This difference tells us that datasets with different structures can have the same correlation coefficient.

### Exercise 4

(Add code and narrative as needed. Note that two R chunks are given but they are not labeled. Use the convention from above to name them appropriately.)

```{r}


```

```{r}


```

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, with the green +C.)
